---
title: "Introduction to QPLOT"
author: "via Udemy"
date: "29/09/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
 
## Description

Qplot part of ggplot2 (and both can work with dataframes). Price Wars data set gathered by AGJ.

## Packages + Data

```{r}
library(ggplot2)
library(dplyr)
library(gsheet)
library(vembedr)
library(gridExtra)
library("htmltools")
df <- gsheet2tbl('https://drive.google.com/open?id=1_6RZ0HXg7VbgO78oyFfUyZaFOUHYWijy8XH1_jw5tA4')
```

## Using QPLOT - basic, count for one attribute
Pass qplot some data (first argument), with one attribute from data set - gives histogram in this case.

```{r}
qplot(data=ds, x=Coles)
```

## Using QPLOT - show values from multiple attibutes
Pass qplot some data (first argument), with an attribute. Gives histogram in this case.

```{r}
qplot(data=ds, x=Coles, y=ds$`Allocated Category`)
```

# To set aesthetics, wrap in I()
If not wrapped in I, qplot will try to 'wrap'.
```{r}
qplot(data=ds, x=Coles, y=ds$`Allocated Category`, size=I(5))
```

# To set aesthetics, wrap in I()
If not wrapped in I, qplot will try to 'wrap'.
```{r}
qplot(data=ds, x=Coles, y=ds$`Allocated Category`, size=I(2), colour=I("Blue"))
```

# Change the geometry
From what is default to box plot. PROBLEM - only shows lines (not correct box plots) FLIP THE x and y (not the catergorical data).
```{r}
qplot(data=ds, x=Coles, y=ds$`Allocated Category`, geom="boxplot")
```

# Change the geometry - for box, x = categorical, y = continuous!!!
From what is default to box plot. PROBLEM - only shows lines (not correct box plots) FLIP THE x and y.
```{r}
qplot(data=ds, x=ds$`Allocated Category`, y=Coles, geom="boxplot")
```

# Change the geometry - Bar Graph

```{r}
qplot(data=ds, x=ds$`Allocated Category`, stat ="count", colour=ds$`Allocated Category`)
```


```{r}

```



