---
title: "Visualizing what we need"
author: "via Udemy"
date: "29/09/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
 
## Description

Qplot part of ggplot2 (and both can work with dataframes). Price Wars data set gathered by AGJ.

## Packages + Data

```{r}
library(ggplot2)
library(dplyr)
library(gsheet)
library(vembedr)
library(gridExtra)
library("htmltools")
df <- gsheet2tbl('https://drive.google.com/open?id=1_6RZ0HXg7VbgO78oyFfUyZaFOUHYWijy8XH1_jw5tA4')
```

# Scatter using two numerical values

In black we have no way of determining if from Coles or WW...

```{r}
qplot(data=ds, x=Coles, y=Woolworths, main = 'Woolworths versus Coles Full Price Scatter Plot',  ylab = 'Woolworths Items (AUD)', xlab = 'Coles Items (AUD)')
```

```{r}
qplot(data=ds, x=ds$`Coles Sale`, y=ds$`Woolworths Sale`, main = 'Woolworths Sale versus Coles Sale Scatter Plot',  ylab = 'Woolworths Sale Items (AUD)', xlab = 'Coles Sale Items (AUD)')
```

Again - in black, we have no way of determining if the items are from Coles or WW

# Scatter - adjust size
Recall - "Mapping is when we are assigning a parameter"

```{r}
qplot(data=ds, x=ds$`Coles Sale`, y=ds$`Woolworths Sale`, size = I(1), main = 'Woolworths Sale versus Coles Sale Scatter Plot',  ylab = 'Woolworths Sale Items (AUD)', xlab = 'Coles Sale Items (AUD)')
```

# Scatter - same colour for all

```{r}
qplot(data=ds, x=ds$`Coles Sale`, y=ds$`Woolworths Sale`, colour = I("Red"), size = I(1), main = 'Woolworths Sale versus Coles Sale Scatter Plot',  ylab = 'Woolworths Sale Items (AUD)', xlab = 'Coles Sale Items (AUD)')
```

# Scatter - mapping colour

```{r}
qplot(data=ds, x=Coles, y=Woolworths, colour = ds$`Allocated Category`, main = 'Woolworths versus Coles Full Price Scatter Plot',  ylab = 'Woolworths Items (AUD)', xlab = 'Coles Items (AUD)') + theme(legend.title=element_blank())
```


```{r}
qplot(data=ds, x=ds$`Coles Sale`, y=ds$`Woolworths Sale`, colour = ds$`Allocated Category`, main = 'Woolworths Sale versus Coles Sale Scatter Plot',  ylab = 'Woolworths Sale Items (AUD)', xlab = 'Coles Sale Items (AUD)') + theme(legend.title=element_blank())
```

```{r}
qplot(data=ds, x=ds$`Woolworths Sale`, y=Woolworths, colour = ds$`Allocated Category`, main = 'Woolworths Sale Price versus Woolworths Full Price Scatter Plot',  ylab = 'Full Price Items (AUD)', xlab = 'Sale Items (AUD)') + theme(legend.title=element_blank())
```

```{r}
qplot(data=ds, x=ds$`Coles Sale`, y=Coles, colour = ds$`Allocated Category`, main = 'Coles Sale Price versus Coles Full Price Scatter Plot',  ylab = 'Full Price Items (AUD)', xlab = 'Sale Items (AUD)') + theme(legend.title=element_blank())
```

