---
title: "Visualization with GGPLOT"
author: "via Udemy"
date: "30/09/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages + Data

```{r}
library(ggplot2)
library(dplyr)
library(gsheet)
library(vembedr)
library(gridExtra)
library("htmltools")
df <- gsheet2tbl('https://drive.google.com/open?id=1_6RZ0HXg7VbgO78oyFfUyZaFOUHYWijy8XH1_jw5tA4')
```

## GGPLOT Function

Lots of power and flexibility for visualization! superdatascience.com/datavisualization download (but will use Coles and Woolworths data set). Aesthetics - the mapping of data to the chart. Statistical transformation = doing something to your data that will enable you to visualize it in some way (eg histogram will inherently perform counts / establish density).

```{r}
# Grammar of Graphics

```

## Aesthetics
Most basic form contains specify data set, and the aesthetic for mapping the data to the function. 
```{r}
ggplot(data=ds, aes(x=ds$'Allocated Category', y=Coles))
```

## Aesthetics + Geometry
```{r}
ggplot(data=ds, aes(x=ds$'Allocated Category', y=Coles)) + geom_boxplot()
```


## Aesthetics + Geometry + Colour
```{r}
ggplot(data=ds, aes(x=ds$'Allocated Category', y=Coles, colour = ds$`Allocated Category`)) + 
  geom_boxplot()
```

## Aesthetics + Geometry + Colour (inside)
```{r}
ggplot(data=ds, aes(x=ds$'Allocated Category', y=Coles, fill = ds$`Allocated Category`)) + 
  geom_boxplot() + theme(legend.title=element_blank())
```

## Aesthetics + Geometry + Colour (inside) + SIZE mapping
```{r}
ggplot(data=ds, aes(x=ds$'Allocated Category', y=Coles, size = Amount, colour = ds$`Allocated Category`)) + 
  geom_point() + theme(legend.title=element_blank())
```

## LAYERS + Geometry + Colour (inside) + Labels
```{r}
colesHist <- ggplot(data=ds, aes(x=ds$'Allocated Category', y=Coles, fill = ds$`Allocated Category`))
colesHist + geom_boxplot() + theme(legend.title=element_blank()) + labs(title = "test", x = "xtest") 
```

```{r}
colesSaleHist <- ggplot(data=ds, aes(x=ds$'Allocated Category', y=ds$`Coles Sale`, colour = ds$`Allocated Category`))
colesSaleHist + geom_jitter(size = 0.6) + geom_boxplot(alpha = 0.5) + theme(legend.title=element_blank()) + labs(title = "test", x = "xtest")
```


## LAYERS + Geometry + Colour (inside) + Labels + ADD LIMITS to SCALE!!! e.g., 0 till 55
```{r}
colesHist <- ggplot(data=ds, aes(x=ds$'Allocated Category', y=Coles, fill = ds$`Allocated Category`)) + geom_boxplot() + theme(legend.title=element_blank()) + labs(title = NULL,  x = "Coles", y = NULL) + coord_flip()
```

```{r}
colesSaleHist <- ggplot(data=ds, aes(x=ds$'Allocated Category', y=ds$`Coles Sale`, fill = ds$`Allocated Category`)) + geom_boxplot() + theme(legend.title=element_blank()) + labs(title = NULL,  x = "Coles Sale", y = NULL) + coord_flip()
```

```{r}
wwHist <- ggplot(data=ds, aes(x=ds$'Allocated Category', y=Woolworths, fill = ds$`Allocated Category`)) + geom_boxplot() + theme(legend.title=element_blank()) + labs(title = NULL,  x = "WW", y = NULL) + coord_flip()
```

```{r}
wwSaleHist <- ggplot(data=ds, aes(x=ds$'Allocated Category', y=ds$`Woolworths Sale`, fill = ds$`Allocated Category`)) + geom_boxplot() + theme(legend.title=element_blank()) + labs(title = NULL, x = "WW Sale", y = NULL) + coord_flip()

#aes_position - Position related aesthetics: x, y, xmin, xmax, ymin, ymax, xend, yend



```

```{r}
grid.arrange(colesHist, colesSaleHist, wwHist, wwSaleHist, nrow = 4) 
#How do you make the absolute size bigger?!?
#theme(plot.margin = unit(c(40, 40, 10, 10)))
```

```{r}
facet_grid(colesHist, colesSaleHist, wwHist, wwSaleHist) 
#How do you make the absolute size bigger?!?
#theme(plot.margin = unit(c(40, 40, 10, 10)))
```


```{r}
grid.arrange(colesHist, colesSaleHist, widths = c(15), heights = c(10, 10), nrow = 2)
#How do you make the absolute size bigger?!?
```

```{r}
grid.arrange(colesHist, colesSaleHist, widths = c(15), heights = c(10, 10), nrow = 2)
#How do you make the absolute size bigger?!?
```

```{r}
colesSaleHist <- ggplot(data=ds, aes(x=ds$'Allocated Category', y=ds$`Coles Sale`, colour = ds$`Allocated Category`))
test2 <- colesSaleHist + geom_jitter(size = 0.6) + geom_boxplot(alpha = 0.5) + theme(legend.title=element_blank()) + labs(title = "test", x = "xtest") + coord_flip()
```

```{r}
grid.arrange(test1, test2)
```

```{r}
#Exploring Unit and Amount - Stacked Histogram
histAll <- ggplot(data=ds, aes(x=ds$Coles, fill = ds$`Allocated Category`))
histAll + geom_histogram() + theme(legend.title=element_blank()) + labs(title = "test", x = "xtest") + facet_grid(ds$`Allocated Category`~.)
```

```{r}
#Exploring Unit and Amount - Stacked Histogram
 <- ggplot(data=ds, aes(x=ds$Coles, fill = ds$`Allocated Category`))
histAll + geom_histogram() + theme(legend.title=element_blank()) + labs(title = "test", x = "xtest") + facet_grid(ds$`Allocated Category`~.)
```



```{r}
ggplot(data=sugarySnack_data, aes(x=sugarySnack_data$'Allocated Category', y=sugarySnack_data$Coles, fill = ds$`Allocated Category`)) + geom_boxplot() + theme(legend.title=element_blank()) + labs(title = NULL, x = NULL, y = NULL) + coord_flip()

```


```{r}
#Exploring Unit and Amount - Data Selection
library(car)
sugarySnack_data$`Woolworths Sale` %>% qqPlot(dist="norm")
```



```{r}
sugarySnack_data$Per1000gPrice_WWSale %>% qqPlot(dist="norm")
```

```{r}
sugarySnack_data$Woolworths %>% qqPlot(dist="norm")
```



```{r}
sugarySnack_data$Per1000gPrice_WW %>% qqPlot(dist="norm")
```


## Padding and Scaling

```{r}
colesHist <- ggplot(data=ds, aes(x=ds$'Allocated Category', y=Coles, fill = ds$`Allocated Category`)) + geom_boxplot() + theme(legend.title=element_blank()) + labs(title = NULL,  x = "Coles", y = NULL) + guides(fill = FALSE) + coord_flip() #Free scaling and padding
colesSaleHist <- ggplot(data=ds, aes(x=ds$'Allocated Category', y=ds$`Coles Sale`, fill = ds$`Allocated Category`)) + geom_boxplot() + theme(legend.title=element_blank()) + labs(title = NULL,  x = "Coles Sale", y = NULL) + guides(fill = FALSE) + coord_flip() + ylim(0,60) #Scaling with padding
wwHist <- ggplot(data=ds, aes(x=ds$'Allocated Category', y=Woolworths, fill = ds$`Allocated Category`)) + geom_boxplot() + theme(legend.title=element_blank()) + labs(title = NULL,  x = "WW", y = NULL) + guides(fill = FALSE) + coord_flip() + ylim(0,60)
wwSaleHist <- ggplot(data=ds, aes(x=ds$'Allocated Category', y=ds$`Woolworths Sale`, fill = ds$`Allocated Category`)) + geom_boxplot() + theme(legend.title=element_blank()) + labs(title = NULL, x = "WW Sale", y = NULL) + guides(fill = FALSE) + coord_flip() + scale_y_continuous(limits = c(0,60), expand = c(0, 0)) #Set scaling and padding
```

```{r}
grid.arrange(colesHist, colesSaleHist, wwHist, wwSaleHist, nrow = 4)
```



